A geo-referenced micro-data set of real estate listings for Spain’s three largest cities

### 2022-07-18 editorial-materials/EPB-2022-0116_response_to_reviewer.Rmd

set.seed(1234)
```
-->

> Dear Authors, Thank you for the opportunity to review your paper. This manuscript is about the publishing of a one-year relocated and randomised listing price data set for three cities in Spain. Both the asking price and coordinates information are anonymised which limits the usefulness of the data for teaching and academic research. Given the house price data is partly from the Idealista company, it is not clear under which kind of licence the data is being issued and to what extent it may be considered open. The unknown quality of this one year randomised data is the main issue for potential users. Having read the paper many times, I believe that the authors have created the idealista18 package (https://github.com/paezha/idealista18). The Idealista18 Github readme file is too simple to guidance users on how to access the data with the R package. So I am not sure it is the right one. The authors are to be commended for their intention to make open real estate data available in an R package which should render it easily accessible for teaching and research. Below is a list of comments and questions that I had which may need to be addressed in future editions of this work.

> 1.	Please reference the package and dataset and include in the text and in the package the license under which the data is released. The Idealista18 github site is unclear on how to access the data with the package.

We really appreciate this suggestion. We have included the license under which the data is distributed in the main text of the introduction. We are also working to publish the dataset via the R package usign CRAN.

@@

> 2.	Please state your anticipated research impacts from the publication of this data set in the introduction.  It would be useful to state how this one-year relocated, and randomised house price data might be best used by academics in research and teaching. The relocated and randomised data may be difficult to further enrich with other variables, the authors need to show how the 44 variables is enough for future users.

Thanks for this comment. We have added discussed these concerns in the introduction.

@@

>5.	It would be useful for the authors to evaluate the datasets in the light of the FAIR guiding principles for research data stewardship (findability, accessibility, interoperability, and reusability).

>6.	Given the asking price has resized the original asking price with a random percentage between -2.5% and +2.5%, please elaborate on how this influences quantitative research results and findings with this data.

>7.	Please kindly add in a usage notes section how this data can be useful for the EPB audience. For example, introduce how this anonymised house price data can be integrated with other data and research.
The original data could be a nice data set for a series of housing related papers. If the authors are unable to publish this original asking price, it maybe worthwhile to publish the research based on this data rather than using the randomised data. House price is locationally sensitive, but both the location and price data in this manuscript are altered by anonymisation. The authors need to show for which analyses the data remains valid despite anonymisation.

We have added some examples of research topics that can be addressed with this dataset  in the introduction.

### 2022-07-18 EPB/EPB.Rmd
Apellido Pelayo
Added comments on license and expected impact

---
title: A geo-referenced micro-data set of real estate listings for Spain’s three largest cities
runninghead: Rey-Blanco \emph{et al}.
author:
- name: D. Rey-Blanco
  num: 1
- name: P. González-Arbues
  num: 1
- name: F. López
  num: 2
- name: A. Páez*
  num: 3
address:
- num: 1
  org: Idealista, Plaza de las Cortes 5, 28014 Madrid, Spain
- num: 2
  org: Facultad de CC de la Empresa, C/ Real, 3. 30201 Cartagena, Murcia, Spain
- num: 3
  org: School of Earth, Environment and Society, McMaster University, 1280 Main St W, Hamilton, Ontario L8S 4K1 Canada
corrauth: "Antonio Páez, School of Earth, Environment and Society, McMaster University, 1280 Main St W, Hamilton, Ontario L8S 4K1 Canada."
email: paezha@mcmaster.ca
abstract: "This article shares an open data product with big geo-referenced micro-data sets of 2018 real estate listings in Spain. These data were originally published on the idealista.com real estate website. The observations were obtained for the three largest cities in Spain: Madrid (n = 94,815 observations), Barcelona (n = 61,486 observations), and Valencia (n = 33,622 observations). The data sets include the coordinates of properties (latitude and longitude), asking prices of each listed dwelling, and several variables of indoor characteristics. The listings were enriched with official information from the Spanish cadastre (e.g., building material quality) plus other relevant geographical features, such as distance to urban points of interest. Along with the real estate listings, the data product also includes neighborhood boundaries for each city. The data product is offered as a fully documented R package and is available for scientific and educational purposes, particularly for geo-spatial studies"
keywords: Housing market; idealista.com; geo-referenced data; point-level data; open data; Spain
classoption:
  - Royal
  - times
bibliography: bibEPB.bib
bibliographystyle: sageh

@@

To overcome these limitations, this paper presents a sort description of an open micro-data set of geo-referenced dwelling listings. The data have been provided by the Idealista company\footnote{Idealista is the major real estate listing website in Spain, and present in other southern european countries as Italy and Portugal} and contain information about 189,923 dwellings located in Spain’s three largest cities. To date, this data product is the biggest open geo-referenced micro-data set of the housing market in Spain. Moreover, the data set has been supplied directly by Idealista, and therefore is clean and free of download errors. The listings have been enriched with official information from the Spanish cadastre along with other relevant geographical features, such as distance to urban points of interest. The data set is distributed as an R package, named ‘idealista18’, which can be accessed from the Github repository\footnote{The direct URL to the GitHub repository is \url{https://github.com/paezha/idealista18}}.

>>>>

---
title: A geo-referenced micro-data set of real estate listings for Spain’s three largest cities
runninghead: Rey-Blanco \emph{et al}.
author:
- name: D. Rey-Blanco
  num: 1
- name: P. Arbues
  num: 1
- name: F. López
  num: 2
- name: A. Páez*
  num: 3
address:
- num: 1
  org: Idealista, Plaza de las Cortes 5, 28014 Madrid, Spain
- num: 2
  org: Facultad de CC de la Empresa, C/ Real, 3. 30201 Cartagena, Murcia, Spain
- num: 3
  org: School of Earth, Environment and Society, McMaster University, 1280 Main St W, Hamilton, Ontario L8S 4K1 Canada
corrauth: "Antonio Páez, School of Earth, Environment and Society, McMaster University, 1280 Main St W, Hamilton, Ontario L8S 4K1 Canada."
email: paezha@mcmaster.ca
abstract: "This article shares an open data product with big geo-referenced micro-data sets of 2018 real estate listings in Spain. These data were originally published on the idealista.com real estate website. The observations were obtained for the three largest cities in Spain: Madrid (n = 94,815 observations), Barcelona (n = 61,486 observations), and Valencia (n = 33,622 observations). The data sets include the coordinates of properties (latitude and longitude), asking prices of each listed dwelling, and several variables of indoor characteristics. The listings were enriched with official information from the Spanish cadastre (e.g., building material quality) plus other relevant geographical features, such as distance to urban points of interest. Along with the real estate listings, the data product also includes neighborhood boundaries for each city. The data product is offered as a fully documented R package and is available for scientific and educational purposes, particularly for geo-spatial studies"
keywords: Housing market; idealista.com; geo-referenced data; point-level data; open data; Spain
classoption:
  - Royal
  - times
bibliography: bibEPB.bib
bibliographystyle: sageh

@@

To overcome these limitations, this paper presents a sort description of an open micro-data set of geo-referenced dwelling listings. The data have been provided by the Idealista company\footnote{Idealista is the major real estate listing website in Spain, and present in other southern european countries as Italy and Portugal} and contain information about 189,923 dwellings located in Spain’s three largest cities. To date, this data product is the biggest open geo-referenced micro-data set of the housing market in Spain. Moreover, the data set has been supplied directly by Idealista, and therefore is clean and free of download errors. However, in order to be able to share publicly the data we have slightly modified some variables by applying some random noise which will not bias the main results derived from its usage.

This micro-data set is expected to be used as a benchmark dataset to test empirical methods in a reproducible fashion. Applied and theoretical researchers on Real Estate Mass Appraisal and Valuation methods might use this dataset to canonically compare the performance of their proposed comparable and hedonic models, among others. This can also be used to study the segmentation of housing submarkets and related topics such as the impact of suburban areas on house prices. The listings have been enriched with official information from the Spanish cadastre along with other relevant geographical features, such as distance to urban points of interest. In any case, the data might be easily extended by spatially joining other datasets that contain information at administrative, census tract, or postal code levels.

The data set is distributed as an R package, named ‘idealista18’, which can be accessed from the Github repository\footnote{The direct URL to the GitHub repository is \url{https://github.com/paezha/idealista18}}. The database idealista18 is made available under the \href{http://opendatacommons.org/licenses/odbl/1.0/}{Open Database License}. We also share the randomisation process applied to the original dataset in the aforementioned Github repository for full transparency on the data collection process.
